---
title: "Diffusion of Work Injury Law"
output: html_notebook
---

*overview: steps in this script*

1. read networks. All data should already be standardized
       a) cultural spheres 
       b) trade networks
       c) colonial ties (cross-sectional) => will be changed?
       b) distance/prox. between capitals (cross-sectional)

 2. read explanatory variables, basics
 3. read years of >social policy introduction< for each project
 4. create netdiffuseR objects => generate plots if you like#      repeat 4. for each network!
 5. get the respective exposure variables and time-of-adoption (toa)
 6. create process-time control
 7. combine the relevant information into one data frame
 8. !! estimate discrete-time logistic hazard model !!

```{r setup}

# Clean up environment
rm(list = ls(all = T))

# note you must have pacman installed for this to run
# install.packages('pacman')
# library('pacman')

pacman::p_load('netdiffuseR','stargazer','tidyverse','dplyr','countrycode')

# set up a working directory
# Recommended to set up in C:/GitHub/work_inj_diffuse/

wd <- "C:/GitHub/work_inj_diff"


# this is a function to load and save files from the working directory
wdir <- function(x){
  paste(wd,x, sep = "/")
}

```

## Get Data

#### Networkdata sources

http://www.barkhof.uni-bremen.de/~mwindzio/edgelist_cultural_spheres.zip
http://www.barkhof.uni-bremen.de/~mwindzio/COW_trade_consolidated.zip
http://www.barkhof.uni-bremen.de/~mwindzio/trade_existence_dummy.csv
http://www.barkhof.uni-bremen.de/~mwindzio/capital_distance_edgelist.zip
http://www.barkhof.uni-bremen.de/~mwindzio/vdem_gdp_pc_INTERPOLATED_consolidated.csv
http://www.barkhof.uni-bremen.de/~mwindzio/vdem_regime__INTERPOLATED_consolidated.csv



### 1. Network Data

```{r windzio_data}


#--- 1. Networks here ---------------


#----- 1a) cultural spheres ---------

edgelist_cultural_spheres <- read.csv(wdir("edgelist_cultural_spheres.csv"))
head(edgelist_cultural_spheres)
dim(edgelist_cultural_spheres)

# - ids should be factor variables
edgelist_cultural_spheres$ego_id <- as.factor(edgelist_cultural_spheres$ego_id)
edgelist_cultural_spheres$alter_id <- as.factor(edgelist_cultural_spheres$alter_id)
head(edgelist_cultural_spheres)


#----- 1b) trade network -----------------------------------

trade_dyadic_consolidated <- read.csv(wdir("COW_trade_consolidated.csv"))

trade_dyadic <- trade_dyadic_consolidated
dim(trade_dyadic)
head(trade_dyadic)

summary(trade_dyadic$smoothtotrade)

ddat <- trade_dyadic[is.na(trade_dyadic$smoothtotrade)==FALSE,]
summary(ddat$smoothtotrade)
d <- density(ddat$smoothtotrade)
plot(d)
polygon(d, col="red", border="blue") 

names(trade_dyadic)[names(trade_dyadic)=="iso3_ego"] <- "ego_id"
names(trade_dyadic)[names(trade_dyadic)=="iso3_alter"] <- "alter_id"
head(trade_dyadic)

# - ids should be factor variables
trade_dyadic$ego_id <- as.factor(trade_dyadic$ego_id)
trade_dyadic$alter_id <- as.factor(trade_dyadic$alter_id)


# - NA to 0 and log positive values
trade_dyadic$smoothtotrade[trade_dyadic$smoothtotrade < 0] <- 0
trade_dyadic$smoothtotrade[is.na(trade_dyadic$smoothtotrade)] <- 0

summary(trade_dyadic$smoothtotrade)
head(trade_dyadic)

trade_dyadic$log_value <- ifelse(trade_dyadic$smoothtotrade > 0, log(trade_dyadic$smoothtotrade), 0)
summary(trade_dyadic$log_value)

# -- distribution is still extreme  
d <- density(trade_dyadic$log_value)
plot(d)
polygon(d, col="red", border="blue")
trade_edgelist <- trade_dyadic

# -- trade: is country non-existent in a particular moment? 
# regime type from vdem data
existence <- read.csv(wdir("trade_existence_dummy.csv"), header = TRUE) # actor attributes
head(existence) 
names(existence)[names(existence)=="iso3_ego"] <- "iso3"



#----- 1c) colonial ties from CEPI --

# - this is only a cross-sectional network ! 
# - we think about using a better one
# - if so, you will have to switch to "undirected=FALSE"
# - when creating the diffnet object. But don't care at the moment! 

colonial_ties_edgelist <- read.csv(wdir("colonial_ties_edgelist.csv"))
head(colonial_ties_edgelist)

names(colonial_ties_edgelist)[names(colonial_ties_edgelist)=="iso_o"] <- "ego_id"
names(colonial_ties_edgelist)[names(colonial_ties_edgelist)=="iso_d"] <- "alter_id"

# - ids should be factor variables
colonial_ties_edgelist$ego_id <- as.factor(colonial_ties_edgelist$ego_id)
colonial_ties_edgelist$alter_id <- as.factor(colonial_ties_edgelist$alter_id)
head(colonial_ties_edgelist)
unique(colonial_ties_edgelist$ego_id)
unique(colonial_ties_edgelist$year)
table(colonial_ties_edgelist$colony)
head(colonial_ties_edgelist)

#----------------------------------------------------------
#----- 1d) spatial distance/ prox. of capitals from CEPI --
#----------------------------------------------------------
# - this is only a cross-sectional network ! 

temp <- tempfile()
download.file("http://www.barkhof.uni-bremen.de/~mwindzio/capital_distance_edgelist.zip",temp)
capital_distance_edgelist <- read.csv(unz(temp, "capital_distance_edgelist.csv"))
unlink(temp)


# --  we use log of proximity
capital_distance_edgelist$log_dist <- log(capital_distance_edgelist$capdist)
log(7593.042) # => 8.934988, ok
capital_distance_edgelist$log_proximity <- 1/(capital_distance_edgelist$log_dist)
1/8.934988 # => 0.1119196,  ok
head(capital_distance_edgelist)
# capital_distance_edgelist <- subset(capital_distance_edgelist, select = -c(log_proximity) )
capital_distance_edgelist$proximity <- 1/(capital_distance_edgelist$capdist)

capital_distance_edgelist <- subset(capital_distance_edgelist,  select=c(ego, alter, year,proximity))

names(capital_distance_edgelist)[names(capital_distance_edgelist)=="ego"] <- "ego_id"
names(capital_distance_edgelist)[names(capital_distance_edgelist)=="alter"] <- "alter_id"

# - ids should be factor variables
capital_distance_edgelist$ego_id <- as.factor(capital_distance_edgelist$ego_id)
capital_distance_edgelist$alter_id <- as.factor(capital_distance_edgelist$alter_id)


```

### 2. Explanatory Variables

```{r explanatory_vars}

#--- 2. explanatory variables -------


# --- we just use gdp and regime-type in this introduction

# GDP from vdem data
gdp <- read.csv(wdir("vdem_gdp_pc_INTERPOLATED_consolidated.csv"), header = TRUE) # actor attributes
head(gdp) 

names(gdp)[names(gdp)=="filled_vdem_gdp_interpol"] <- "gdp" # it's just gdp

# regime type from vdem data
regime <- read.csv(wdir("vdem_regime__INTERPOLATED_consolidated.csv"), header = TRUE) # actor attributes
head(regime) 
regime <- subset(regime, select=c(iso3, year,regime))

#-- merge here ----
covar_base <- subset(gdp, select=c(iso3, year,gdp)) 
head(covar_base)  

covar_base <- merge(covar_base, regime,by=c("iso3","year")) 
head(covar_base)

table(covar_base$year) # - every year on board, for 164 countries
table(covar_base$iso3) # - every country on board, for 131 years
```

### 3. Policy Variables (SFB 1342)

#### SFB Project sources

http://www.barkhof.uni-bremen.de/~mwindzio/A02_unemployment_new.csv
http://www.barkhof.uni-bremen.de/~mwindzio/A03_data.csv
http://www.barkhof.uni-bremen.de/~mwindzio/A04_HCS_toa.csv
http://www.barkhof.uni-bremen.de/~mwindzio/A04_sickness_toa.csv
http://www.barkhof.uni-bremen.de/~mwindzio/A05_edu_intro_comp_schooling.csv
http://www.barkhof.uni-bremen.de/~mwindzio/a06_int.csv

```{r sfb_vars}

# ----- Project A 02 -----------------

# Introduction of unemployment programme
A02_unemployment <- read.csv(wdir("A02_unemployment_new.csv"), header = TRUE) 

# Introduction of work regulations
A02_workinj <- read.csv(wdir("A02_workinj.csv"), header = TRUE)

#This frame only starts in 1880 so we trim our data 
# for now but need to expand the range later

A02_workinj <- A02_workinj %>%
mutate(labor_workinjury_firstlaw = ifelse(labor_workinjury_firstlaw < 1880, 1880, labor_workinjury_firstlaw))

#       year = ifelse(year > max(labor_workinjury_firstlaw), NA, year)
#)

#A02_workinj <- subset(A02_workinj, year < 2005)

# ----- Project A 03 -----------------

# ILO convention ratification data
A03_data <- read.csv(wdir("A03_data.csv"), header = TRUE) 


# ----- Project A 04 -----------------

# Introduction of health care system
A04_HCS_toa <- read.csv("A04_HCS_toa.csv", header = TRUE) 


# Introduction of sickness legislation
A04_sickness_toa <- read.csv(wdir("A04_sickness_toa.csv"), header = TRUE) 


# ----- Project A 05 -----------------

# ---- Introduction of compulsary education

A05_edu_intro_comp_schooling <- read.csv(wdir("A05_edu_intro_comp_schooling.csv"), header = TRUE) 


# ----- Project A 06 -----------------

# Introduction of family legislation
A06_int <- read.csv(wdir("a06_int.csv"), header = TRUE) # actor attributes



covar_ <- data.frame(covar_base)
head(covar_)

A02 <- data.frame(subset(  A02_unemployment, select = c(iso3,unemp_firstlaw,year)  ))
covar_ <- merge(covar_, A02,by=c("iso3","year")) 
head(covar_)
names(covar_)[names(covar_)=="unemp_firstlaw"] <- "toa_unemp_A02"
# head(covar_)

A02_2 <- data.frame(subset(  A02_workinj, select = c(iso3,labor_workinjury_firstlaw,year)  ))
covar_ <- merge(covar_, A02_2,by=c("iso3","year")) 
# head(covar_)
names(covar_)[names(covar_)=="labor_workinjury_firstlaw"] <- "toa_workinj_A02"
# head(covar_)

A03 <- data.frame(subset(  A03_data, select = c(iso3,toa,year)  ))
covar_ <- merge(covar_, A03,by=c("iso3","year")) 
names(covar_)[names(covar_)=="toa"] <- "toa_ILO_A03"
# head(covar_)

A04 <- data.frame(subset(  A04_HCS_toa, select = c(iso3,toa,year)  ))
covar_ <- merge(covar_, A04,by=c("iso3","year")) 
# head(covar_)
names(covar_)[names(covar_)=="toa"] <- "toa_HCS_A04"
# head(covar_)

A04 <- data.frame(subset(  A04_sickness_toa, select = c(iso3,toa,year)  ))
covar_ <- merge(covar_, A04,by=c("iso3","year")) 
# head(covar_)
names(covar_)[names(covar_)=="toa"] <- "toa_sickn_A04"
# head(covar_)


A05 <- data.frame(subset(  A05_edu_intro_comp_schooling, select = c(iso3,toa,year)  ))
covar_ <- merge(covar_, A05,by=c("iso3","year")) 
# head(covar_)
names(covar_)[names(covar_)=="toa"] <- "toa_comp_edu_A05"
# head(covar_)

A06 <- data.frame(subset(  A06_int, select = c(iso3,toa_ml,year)  ))
covar_ <- merge(covar_, A06,by=c("iso3","year")) 
# head(covar_)
names(covar_)[names(covar_)=="toa_ml"] <- "toa_ml_A06"
# head(covar_)

A06 <- data.frame(subset(  A06_int, select = c(iso3,toa_fa,year)  ))
covar_ <- merge(covar_, A06,by=c("iso3","year")) 
# head(covar_)
names(covar_)[names(covar_)=="toa_fa"] <- "toa_fa_A06"
# head(covar_)

covar_ <- merge(covar_, existence,by=c("iso3","year")) 
head(covar_)

covar <- covar_
dim(covar)
unique(covar$iso3)
unique(covar$year)
unique(edgelist_cultural_spheres$year)

head(covar)
# - combined covar object for all explanatory variables
# - covar$gdp & covar$regime



```


## 4. netdiffuseR setup
  


keep in mind what we have for each project
  -     >>toas<<:
  - A 01:
  - A 02: toa_unemp_A02
  - A 03: toa_ILO_A03
  - A 04: toa_HCS_A04 and toa_sickn_A04
  - A 05: toa_comp_edu_A05
  - A 06: toa_ml_A06 and toa_fa_A06

keep in mind which networks we have
  -     >>edgelists<<: 
  - trade_edgelist                => trade network
  - edgelist_cultural_spheres     => cultural spheres
  - colonial_ties_edgelist        => colonial ties
  - capital_distance_edgelist    => d = distance , prox. = 1/d
  - make netdiffuse object: combine edgelist with covariate object
  - begin with cultural spheres
  

```{r 4_netdiff}
# -------------------------
# - 4a) cultural spheres --
# -------------------------
# - here comes the core: creating the diffnet object
head(edgelist_cultural_spheres)
dim(edgelist_cultural_spheres)
diffnet_culture <- edgelist_to_diffnet(
  edgelist = edgelist_cultural_spheres[,1:2], # As usual, a two column dataset [,1:2]
  w        = edgelist_cultural_spheres$weight,
  t0       = edgelist_cultural_spheres$year,  # An integer vector with starting point of spell
  t1       = edgelist_cultural_spheres$year,  # An integer vector with the endpoint of spell
  undirected = TRUE,        # undirected network
  dat      = covar,         # Attributes dataset
  idvar    = "iso3",                  
  toavar   = "toa_workinj_A02",          # -- !! here just change time-of-adoption !! -- #
  timevar  = "year",
  keep.isolates = TRUE    # Keeping isolates (if there's any)
)
diffnet_culture
plot(diffnet_culture)
summary(diffnet_culture)

# -------------------------------------------------------------------------
# -- 5. get the respective exposure variables and time-of-adoption (toa)
# -- generate exposure and add to diffnet object
diffnet_culture[["lag_w_expo_culture"]] <- exposure(diffnet_culture, valued = T, lags = 1)#
diffnet_culture[["lag_expo_culture"]] <- exposure(diffnet_culture, valued = F, lags = 1)
diffnet_culture[["adopted"]]  <- toa_mat(diffnet_culture)$cumadopt

table(data.frame(diffnet_culture)$adopted) # don't care about no. adopted here
summary(data.frame(diffnet_culture)$lag_w_expo_culture)
head(data.frame(diffnet_culture)) # exposure is NA for 1st 164 cases => 1880
tail(data.frame(diffnet_culture))


# -------------------------
# - 4b) colonial ties -----
# -------------------------
# - here comes the core: creating the diffnet object
head(colonial_ties_edgelist)
dim(colonial_ties_edgelist)
diffnet_colony <- edgelist_to_diffnet(
  edgelist = colonial_ties_edgelist[,1:2], # As usual, a two column dataset [,1:2]
  w        = colonial_ties_edgelist$colony,
  t0       = colonial_ties_edgelist$year,  # An integer vector with starting point of spell
  t1       = colonial_ties_edgelist$year,  # An integer vector with the endpoint of spell
  undirected = TRUE,        # !!! change for >directed< network !!! => we provide it later
  dat      = covar,         # Attributes dataset
  idvar    = "iso3",                  
  toavar   = "toa_workinj_A02",          # -- !! here just change time-of-adoption !! -- #
  timevar  = "year",
  keep.isolates = TRUE    # Keeping isolates (if there's any)
)
diffnet_colony
plot(diffnet_colony)
summary(diffnet_colony)

# -------------------------------------------------------------------------
# -- 5. get the respective exposure variables and time-of-adoption (toa)
# compute exposure: Netdiffuser automatically identifies whether the input is dynamic or not.
diffnet_colony[["lag_w_expo_colony"]] <- exposure(diffnet_colony, valued = T, lags = 1)
diffnet_colony[["lag_expo_colony"]] <- exposure(diffnet_colony, valued = F, lags = 1)

diffnet_colony[["adopted"]]  <- toa_mat(diffnet_colony)$cumadopt

diffnet_colony
summary(diffnet_colony)
summary(data.frame(diffnet_colony)$lag_w_expo_colony)

# -------------------------
# - 4c) trade network -----
# -------------------------
# - here comes the core: creating the diffnet object
head(trade_edgelist)
dim(trade_edgelist)
diffnet_trade <- edgelist_to_diffnet(
  edgelist = trade_edgelist[,1:2], # As usual, a two column dataset [,1:2]
  t0       = trade_edgelist$year,  # An integer vector with starting point of spell
  t1       = trade_edgelist$year,  # An integer vector with the endpoint of spell
  w        = trade_edgelist$log_value,
  undirected = TRUE,        # undirected network
  dat      = covar,         # Attributes dataset
  idvar    = "iso3",                  
  toavar   = "toa_workinj_A02",          # -- !! here just change time-of-adoption !! -- #
  timevar  = "year",
  keep.isolates = TRUE    # Keeping isolates (if there's any)
)
diffnet_trade
plot(diffnet_trade)
summary(diffnet_trade)


# -------------------------------------------------------------------------
# -- 5. get the respective exposure variables and time-of-adoption (toa)
# compute exposure: Netdiffuser automatically identifies whether the input is dynamic or not.
diffnet_trade[["lag_w_expo_trade"]] <- exposure(diffnet_trade, valued = T, lags = 1)
diffnet_trade[["lag_expo_trade"]] <- exposure(diffnet_trade, valued = F, lags = 1)

diffnet_trade[["adopted"]]  <- toa_mat(diffnet_trade)$cumadopt

head(data.frame(diffnet_trade))
tail(data.frame(diffnet_trade))
summary(data.frame(diffnet_trade)$lag_w_expo_trade)


# -----------------------------
# - 4d) spatial proximity -----
# -----------------------------
# - here comes the core: creating the diffnet object
head(capital_distance_edgelist)
dim(capital_distance_edgelist)
diffnet_proximity <- edgelist_to_diffnet(
  edgelist = capital_distance_edgelist[,1:2], # As usual, a two column dataset [,1:2]
  t0       = capital_distance_edgelist$year,  # An integer vector with starting point of spell
  t1       = capital_distance_edgelist$year,  # An integer vector with the endpoint of spell
  w        = capital_distance_edgelist$proximity,
  undirected = TRUE,        # undirected network
  dat      = covar,         # Attributes dataset
  idvar    = "iso3",                  
  toavar   = "toa_workinj_A02",          # -- !! here just change time-of-adoption !! -- #
  timevar  = "year",
  keep.isolates = TRUE    # Keeping isolates (if there's any)
)
diffnet_proximity
plot(diffnet_proximity)
summary(diffnet_proximity) # - moran's I seems to be insignificant regarding
                           # - >unweighted< geodesic distance in network.
                           # - Unweighted network density is 100% => it's not a variable
                           # - but see hazard model below with 
                           # - with >exposure< by >weighted< distances!

diffnet_proximity[["lag_w_expo_proximity"]] <- exposure(diffnet_proximity, valued = T, lags = 1)

diffnet_proximity[["lag_expo_proximity"]] <- exposure(diffnet_proximity, valued = F, lags = 1)

diffnet_proximity[["adopted"]]  <- toa_mat(diffnet_proximity)$cumadopt

diffnet_proximity
summary(data.frame(diffnet_proximity)$lag_expo_proximity)
head(data.frame(diffnet_proximity))

# - save first diffnet object as data as data frame
diff_data_culture <- as.data.frame(diffnet_culture)
head(diff_data_culture)
table(diff_data_culture$adopted) # don't care about n. of cases

```
```{r six}
# -----------------------------------------------------------------
# -----------------------------------------------------------------
# - 6. create process-time control, define the duration of episode
# -----------------------------------------------------------------
# -----------------------------------------------------------------

diff_data_culture$t <- (diff_data_culture$per - 1880 )
summary(diff_data_culture$t)

# -- create time periods for stepwise PC Rate model
summary(diff_data_culture$t)
diff_data_culture$t0_25 <- ifelse(diff_data_culture$t < 25, 1, 0)
diff_data_culture$t25_49 <- ifelse(diff_data_culture$t >= 25 
                                   & diff_data_culture$t < 50, 1, 0)
diff_data_culture$t50_74 <- ifelse(diff_data_culture$t >= 50 
                                   & diff_data_culture$t < 75, 1, 0)
diff_data_culture$t75_99 <- ifelse(diff_data_culture$t >= 75 
                                   & diff_data_culture$t < 100, 1, 0)
diff_data_culture$t100_130 <- ifelse(diff_data_culture$t >= 100, 1, 0)
```

```{r seven}
# -----------------------------------------------------------
# -- 7. combine the relevant information into one data frame
# -----------------------------------------------------------
# --- merge exposure from other networks --------------------
# -----------------------------------------------------------

diff_data <- diff_data_culture

head(diff_data)
diffnet_colony <- data.frame(diffnet_colony)
diffnet_trade <- data.frame(diffnet_trade)
diffnet_proximity <- data.frame(diffnet_proximity)

# -------------------------------------------------------
# -------------- merge everthing together ---------------
# -------------------------------------------------------
# --- merge id is now "id",  automatically generated in netdiffuseR objects
d <- subset(  diffnet_colony, select = c(id,per,lag_w_expo_colony, lag_expo_colony)  )
diff_data <- merge(diff_data, d,by=c("id","per")) 
d <- subset(  diffnet_trade, select = c(id,per,lag_w_expo_trade, lag_expo_trade)  )
diff_data <- merge(diff_data, d,by=c("id","per")) 
d <- subset(  diffnet_proximity, select = c(id,per,lag_w_expo_proximity, lag_expo_proximity)  )
diff_data <- merge(diff_data, d,by=c("id","per")) 

head(diff_data)

# - distribution of network, range and "density/edge weight" => 164 NAs for 1880
summary(diff_data$lag_w_expo_culture)
summary(diff_data$lag_w_expo_colony)
summary(diff_data$lag_w_expo_trade)
summary(diff_data$lag_w_expo_proximity)

summary(diff_data$adopted) # - create new for each project specific-toa
diff_data$gdp10000 <- diff_data$gdp/10000 # in 10,000 USD

```

```{r }
# -----------------------------------------------------------------
# -----------------------------------------------------------------
# - 8. !! estimate discrete-time logistic hazard model !!
# -----------------------------------------------------------------
# -----------------------------------------------------------------
# --- check cases never in risk set
# --- check toa 1880 !!!
# head(diff_data)

model1 <- glm(adopted ~ 
              + t0_25 
              + t25_49 
              + t50_74 
              + t75_99 
              + t100_130  
              + existence
              + lag_w_expo_culture 
              + lag_w_expo_colony
              + lag_w_expo_trade
              + gdp10000
              + regime
              + 0,
      dat    = diff_data, 
      subset = (per <= toa), # - extremely important !
      family = binomial(link="logit"))
summary(model1)
exp(coef(model1))

model2 <- glm(adopted ~ 
                + t0_25 
              + t25_49 
              + t50_74 
              + t75_99 
              + t100_130  
              + existence
              + lag_w_expo_culture 
              + lag_w_expo_colony
              + lag_w_expo_trade
              + lag_w_expo_proximity
              + gdp10000
              + regime
              + 0,
              dat    = diff_data, 
              subset = (per <= toa),
              family = binomial(link="logit"))
summary(model2)
exp(coef(model2))



stargazer(model1,model2,
          type = "html", 
          title = "Global Network Diffusion of Compulsory Education",
          dep.var.labels=c("Introduction of Work-Injury Law"),
          covariate.labels=c("rate t(0-24)", 
                             "rate t(25-49)",
                             "rate t(50-74)",
                             "rate t(75-99)",
                             "rate t(100-130)",
                             "state existed (=1,else=0)", 
                             "cultural spheres netw.: w. exposure (lag 1 year)",
                             "colonies netw.: exposure ",
                             "trade net: w. exposure (lag 1 year)",
                             "spatial proximity netw.: w. exposure ",
                             "GDP per capita / 10000 USD",
                             "democratization" 
                             ),
          out=wdir("model_work_inj_A02.htm")) # - create folder, mac users adjust


# ---------------------------------------------
# --- some functions of netdiffuseR, here for 
# --- the cultural spheres network
# ---------------------------------------------

s <- 12345
cols <- c("lightblue","green", "blue")
oldpar <- par(no.readonly = T)
coords <- set.seed(s);plot(diffnet_culture, main="culture & education")


bmp(filename = "c:/data/culture_edu.bmp") # - create folder, mac users adjust
plot_diffnet(diffnet_culture, 
             slices = c(1,50,100,130), layout=coords)
dev.off()

plot_adopters(diffnet_culture, 
              include.legend = FALSE, what = c("adopt", "cumadopt"))
plot_hazard(diffnet_culture, ylim=c(0,1))
plot_infectsuscep(diffnet_culture)

# network threshold: required proportion or number of neighbors that leads you to adopt
plot_threshold(diffnet_culture, undirected = FALSE, vertex.size = 1/5)

# Classify Adopters
diffnet.toa(diffnet_culture)[diffnet_culture$toa==max(diffnet_culture$toa, na.rm = TRUE)] <- NA
out <- classify_adopters(diffnet_culture)
out

# This is one way to combine adopters ad thresholds in one object
round(
  with(out, ftable(toa, thr, dnn=c("Time of Adoption", "Threshold")))/
    nnodes(diffnet_culture[!is.na(diffnet_culture$toa)])*100, digits=2)
ftable(out)

ids <- unique(edgelist_cultural_spheres$ego_id) 
ids <- as.data.frame(ids)

ids1 <- unique(edgelist_cultural_spheres$alter_id) 
ids1 <- as.data.frame(ids1)

colnames(ids1)[1] <- "ids"
ids <- rbind(ids, ids1)
ids <- unique(ids)
ids$ids <- as.character(ids$ids)

ids <- sort(ids)

# Adopter types and threshols combined
thresholds <- cbind(as.data.frame(classify(diffnet_culture)), diffnet_culture$toa, ids)
head(thresholds)
```

